US General Society Survey Analysis

### 2024-03-14 paper/paper.qmd
commiting the small changes before i pull

## Data Explained
There could have been many other similar datasets that could have been used for this project for example we could have chosen to look at the census and election data for Canada. However, our group decided that because part of the analysis was done in @rohan, there were still many other variables that we could explore as we dive furthur into the 2020 presidential election and try to intrepret if there are any correlations between the variables and the result. Our team found it interesting to see all the variables that were collected by the US government and the correlations we saw during the analysis process; where there most definitely was a positive correlation between each variable and the outcome of the votes. Although we are analyzing the 2020 election that has already taken place, the analysis we do in the later sections are believed to apply to the 2024 elections happening this year. This is enough reason for us and the reader to dive into the patterns that exist with this large dataset.

>>>>

## The Destination to Reach with the Data
There could have been many other similar datasets that could have been used for this project for example we could have chosen to look at the census and election data for Canada. However, our group decided that because part of the analysis was done in @rohan, there were still many other variables that we could explore as we dive furthur into the 2020 presidential election and try to intrepret if there are any correlations between the variables and the result. Our team found it interesting to see all the variables that were collected by the US government and the correlations we saw during the analysis process; where there most definitely was a positive correlation between each variable and the outcome of the votes. Although we are analyzing the 2020 election that has already taken place, the analysis we do in the later sections are believed to apply to the 2024 elections happening this year. This is enough reason for us and the reader to dive into the patterns that exist with this large dataset.
